Model Checking for Open Concurrent Systems

### 2018-09-05 2018-ModelCheckingPNets/checking.tex
add pNet packages

@@

@@

 where, $c$ is an action name expressing the communication port. $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$. $p$ is an atomic proposition.  
  {\color{red}{[To do Tengfei: Must complete the explaination ]}}.

@@

{\color{red}{[To do Tengfei: Be more precise]}}

>>>>

%----- pNet macros package
\usepackage{epsfig,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

\usepackage{macrospNets}

@@

\section{Use-case: The BIP Failure-Timer architecture}
\TODO{Describe here the full Failure-Timer architecture, as taken from the Avocs paper, including an informal presentation of the original BIP system, its full translation into a pNet system (pLTSs and pNet nodes), and the generated Open Automaton}
\NOTE{All figures are already available from the Avocs paper sources.}

@@

 where, $c$ is an action name expressing the communication port. $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$. $p$ is an atomic proposition.  
  \TODO{Tengfei: Must complete the explaination}.

@@

\TODO{Tengfei: Be more precise}
